---
title: "Assignment_2"
author: "Tanuj Maithani"
date: "September 25, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(pdftools)
library(tm)
library(topicmodels)
library(tidytext)
```

```{r}
book = pdf_text("ISLR.pdf")
```


```{r}
regex_func = function(x){return(gsub('[^a-z ]','',x))}
common_stop_words = stopwords()
custom_stop_words = c('set','can','get','will','using')
all_stop_words = append(common_stop_words,custom_stop_words)

```

###### Create the corpus using the PDF file and apply standard text cleaning techniques to clean the text :

```{r}
docs = VCorpus(VectorSource(book))
docs = tm_map(docs, content_transformer(tolower))
docs = tm_map(docs, content_transformer(regex_func))
docs = tm_map(docs,stripWhitespace)
docs = tm_map(docs, removeWords, all_stop_words)
```

###### Create the Document Term Matrix from the corpus

```{r}
dtm = DocumentTermMatrix(docs)
df_dtm = as.data.frame(as.matrix(dtm))
dim(df_dtm)
head(df_dtm,10)
```

###### Apply topic modelling using LDA technique with 4 topics and get topic to word matrix and document to topic matrix

```{r}
dtm_nonsparse = removeSparseTerms(dtm,sparse = 0.95)
dtm_nonsparse = dtm_nonsparse[rowSums(as.matrix(dtm_nonsparse))>0,]

lda.out = LDA(dtm_nonsparse,4,method = 'Gibbs')

word2topic = tidy(lda.out, matrix ="beta")
doc2topic = tidy(lda.out, matrix = "gamma")
View(word2topic)
View(doc2topic)
```

###### Plot the top 5 words across each topic as bar charts

```{r}
library(dplyr)
library(ggplot2)
word2topic %>% group_by(topic) %>% arrange(topic,-beta) %>% top_n(5) %>% ungroup() %>% 
  ggplot(aes(x=reorder(term, beta), y=beta)) + geom_bar(stat='identity') + facet_wrap(~topic, scales='free') + coord_flip()
```


###### Plot topic wise no. of documents in a simple bar chart (i.e no. of pages in our examples)

```{r}
doc2topic %>% group_by(document) %>%arrange(document,-gamma)%>% top_n(1) %>%
  group_by(topic) %>% summarise(documents=n()) %>%
  ggplot(aes(x=topic, y=documents)) + geom_bar(stat="identity")
```







